{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-11 Paper/main.tex
iid errorterm rearrangement, unifying stuff in NIR appendix

		 We created two different error-terms by generating an i.i.d. standard normal error term and multiplying it by two error variations $\sigma_e $. The error variations represent different signal-to-noise ratios of the responses to test the methods with low and high amounts of noise in the responses. They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.	
		\begin{equation}
			\begin{split}
				Y_{1,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{orig}, f\rangle)}{0.9} - var(\langle NIR_{orig}, f\rangle)\biggr\rbrack \\
				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{orig}, f\rangle)}{0.6} - var(\langle NIR_{orig}, f\rangle)\biggr\rbrack
			\end{split}
		\end{equation}

		Here, $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations, using the two coefficient functions and the two error terms. These four combinations are then used with a different number of Monomial basis functions, cubic B-spline basis functions and Fourier basis functions to predict the generated responses using the basis expansion approach and the FPCR approach.\\

@@

	\subsection{Near-infrared (NIR) Spectroscopy}\label{NIR}
	NIR- spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm). It measures the absorption and interaction of this spectrum of radiation with the sample. NIR-spectroscopy is not only faster and cheaper than the standard test procedure – another significant advantage is that it does not need a reagent and thus does not destroy the sample. It is used for analysis in different sectors and fields, like the agrochemical industry and healthcare. Its non-invasive nature makes it also an asset for medical applications like the monitoring of diabetes in which NIR-spectroscopy can detect the worsening of the blood glucose metabolic dysfunction (cf . \cite{FR_li_et_al_2020}). \\
	In the context of this paper, the gasoline data set which is used for the simulation and the application is constructed using NIR spectroscopy. According to \cite{Bohacs_Ovadi_Salgo1998} NIR-spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules). While this paper focuses on the prediction of the octane number of gasoline, other research focuses  on different properties of gasoline such as the olefin, naphtaenic and aromatic content (Parisi et al. 1990, as cited in \cite{Bohacs_Ovadi_Salgo1998}) or the distillation characteristics (Pauls 1985, as cited in \cite{Bohacs_Ovadi_Salgo1998})
	\vspace{0.5cm}

>>>>

		 We created two different error-terms by generating an i.i.d. standard normal error term 	$Z \sim \mathcal{N}(0,1)$ and multiplying it by two error variations $\sigma_e $. The error variations represent different signal-to-noise ratios of the responses to test the methods with low and high amounts of noise in the responses. They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.	
		\begin{equation}
			\begin{split}
				Y_{1,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{orig}, f\rangle)}{0.9} - var(\langle NIR_{orig}, f\rangle)\biggr\rbrack \\
				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{orig}, f\rangle)}{0.6} - var(\langle NIR_{orig}, f\rangle)\biggr\rbrack
			\end{split}
		\end{equation}

		 In total, we created four combinations, using the two coefficient functions and the two error terms. These four combinations are then used with a different number of Monomial basis functions, cubic B-spline basis functions and Fourier basis functions to predict the generated responses using the basis expansion approach and the FPCR approach.\\

@@

	\subsection{Near-infrared (NIR) Spectroscopy}\label{NIR}
	NIR spectroscopy is a spectroscopic method that uses the near-infrared region of the electromagnetic spectrum (From 780 nm to 2500 nm). It measures the absorption and interaction of this spectrum of radiation with the sample. NIR spectroscopy is not only faster and cheaper than the standard test procedure – another significant advantage is that it does not need a reagent and thus does not destroy the sample. It is used for analysis in different sectors and fields, like the agrochemical industry and healthcare. Its non-invasive nature makes it also an asset for medical applications like the monitoring of diabetes in which NIR spectroscopy can detect the worsening of the blood glucose metabolic dysfunction (cf . \cite{FR_li_et_al_2020}). \\
	In the context of this paper, the gasoline data set which is used for the simulation and the application is constructed using NIR spectroscopy. According to \cite{Bohacs_Ovadi_Salgo1998}, NIR spectroscopy is a feasible method for the analysis of gasoline since most of the absorption that is observed within the described interval of wavelengths is due to overtones and interactions of the radiation with chemical combinations (carbon–hydrogen, carbon–carbon, carbon–oxygen, carbonyl associated groups, aromatic stretching, and deformation vibration of the hydrocarbon molecules). While this paper focuses on the prediction of the octane number of gasoline, other research focuses  on different properties of gasoline such as the olefin, naphtaenic and aromatic content (Parisi et al. 1990, as cited in \cite{Bohacs_Ovadi_Salgo1998}) or the distillation characteristics (Pauls 1985, as cited in \cite{Bohacs_Ovadi_Salgo1998})
	\vspace{0.5cm}
